Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-19 Article/ici_submm_cloudcorr.tex
Work on Section 2.

\newcommand{\todo}[1]{{\color{red} #1}}

@@

The approach is demonstrated on a combination of 183\,GHz channels (following
\citet{buehler:aclou:07}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as AWS, presented below). \todo{Explain what sub-mm can
  do}.}

@@

\subsection{QRNN}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).

\subsubsection{Theory}

\subsubsection{Evaluation metrics}

Quantile loss function

CRPS

@@

\subsubsection{ QRNN model configurations}
%
\label{QRNN_models}

In the study, three types of QRNN models are formulated. For each type, the target is always one of the available 183\,GHz channels, and this target channel is always included in the training set. The choice of other channels in the training set depends on the type of QRNN model chosen. A summary of the three QRNN models described in this study is provided in Table~\ref{tab:QRNN_models}.

@@

\subsection{ICI}
\subsubsection{Example results}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
	\caption{Posterior distribution obtained from QRNN-single (I2V) for three different cases. }
	\label{fig:posterior_distribution_I2V}	
\end{figure}
%f
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
	\label{fig:PDF_predictions}	
\end{figure*}
QRNN predictions are estimates of the posterior distribution over different quantiles. For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ (Sect.~\ref{sec:qrnn-implementation}). The quantiles are interpreted as probabilistic predictions and can be used to construct a probability distribution of the predictions. Fig.~\ref{fig:posterior_distribution_I2V} exemplifies the posterior distribution predicted by QRNN-single. The three cases shown in the figure have a similar median value but very different spread. The spread of the distributions can also be expressed as the prediction interval. If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval. It is gives the range where the prediction could be located and its length is a measure of the reliability. Among the three cases shown in the figure, the blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability. While the other two cases have longer intervals implying higher fluctuations, or low reliability. The quantiles can also be used to interpret the confidence intervals. For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_1}, y_{\tau_2}]$. For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_2 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$. More on confidence interval is discussed in Sect.~\ref{sec:prediction_uncertainty}.

>>>>

\newcommand{\todo}[1]{{\color{red} #1}}
\newcommand{\ynfcs}{$y_\text{NFCS}}
\newcommand{\y}{\vec{y}}

@@

The approach is demonstrated on a combination of 183\,GHz channels (following
\citet{buehler:aclou:07}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as AWS, presented below). \todo{Explain what sub-mm can
  do}.

@@

\subsection{Quantile regression neural networks}
%
The task that we aim to solve in this study is to predict the NFCS brightness
temperatures $\ynfcs$ at a given $187\unit{GHz}$ channel from a vector of
cloud-contaminated observations $\y$. Since the information-content of the
cloud-contaminated observations is certainly too low to solve this problem
exactly, a probabilistic formulation is appropriate here. The aim thus becomes
to predict the conditional distribution $p(\ynfcs | \y)$ of the NFCS brightness
temperatures $\ynfcs$ given the cloud-contaminated observations $\y$.

As has been shown in \citet{pfreundschuh:aneur:18}, quantile regression neural
networks (QRNN) can be used to solve these type of problems. Instead of a point
prediction, as it is typically performed in regression problems, QRNNs learn to
predict a vector of quantiles, which can be used to approximate the distribution
of the predicted quantity conditional on the network inputs. Using QRNNs to
perform probabilistic cloud correction thus not only allows deriving an estimate
for $\ynfcs$ but also for the error of the corrected observations.

For this application, the predicted percentiles are chosen to be
$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
distribution with mean $\mu$ and standard deviation $\sigma$ the
approximately corresponds to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
estimating the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.
The median is used as point estimate for the corrected $\ynfcs$.

Fig.~\ref{fig:posterior_distribution_I2V} presents examples of the predicted
quantiles for three different corrected observations of the ICI I1V channel. The
three cases have a similar median value but very different spread of the
remaining quantiles. These examples illustrate the case of very similar
corrected observation values (the estimated median) but with different estimated
observation errors.

\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
	\caption{Predicted quantiles of the conditional distribution of $\ynfcs$ for
    the ICI I1C channel.}
	\label{fig:posterior_distribution_I2V}	
\end{figure}
%
\subsubsection{ QRNN model configurations}
%
\label{QRNN_models}

In the study, three different QRNN cloud-correction models with different selections of input observations are
investigated. All models ype, the target is always one of the available 183\,GHz channels, and this target channel is always included in the training set. The choice of other channels in the training set depends on the type of QRNN model chosen. A summary of the three QRNN models described in this study is provided in Table~\ref{tab:QRNN_models}.

@@

@@

\subsection{ICI}
\subsubsection{Example results}
%
%f
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of point estimate NFCS from QRNN-single for channels I1V, I2V and I3V. The corresponding distributions for NFCS simulations are also shown.}
	\label{fig:PDF_predictions}	
\end{figure*}
